---
title: "Classification- Logistic Regression"
output:
  html_document: default
  html_notebook: default
---

### Load required data
```{r, message = FALSE}

library(ISLR)
data(Smarket)
```

### Get a knowhow of Data
```{r}
names(Smarket)

dim(Smarket)

summary(Smarket)

cor(Smarket[, -9])

```

As can be seen, also will be expected- there is a very minimal correlation between the previous day returns, but only Correlation is among the Year and Volume.

#### Let's plot the data
```{r, echo=TRUE}
attach(Smarket)
plot(Volume)
plot(Volume ~ Year)
```

Volume has increased over time, i.e. daily trading increased in between the Years, 2001 and 2005.


### Fit a Logistic Regression
```{r}


glm.fit = glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data=Smarket, family = binomial)
summary(glm.fit)


```

With this model, no predictor seems to have an effective correlation with the Direction. Lag1 has the lowest p-value of all, but is still large to be used as a supporting to declare an association. 

####Let's use coef() to access just the coefficients of the model.

```{r}
coef(glm.fit)

summary(glm.fit)$coef

#to check only p-values:
summary(glm.fit)$coef[, 4]
```

R uses the value as 1 for computing if the market went UP.
```{r}
contrasts(Direction)
```

#### Make a Prediction
```{r}
glm.probs = predict(glm.fit, type="response")
glm.probs[1:10]
```

####For a better inference, let's map the probabilities to "Up" or "Down".

```{r}
glm.pred = rep("Down", 1250)
glm.pred[glm.probs > 0.5] = "Up"

table(glm.pred, Direction)

(507 + 145)/1250

mean(glm.pred==Direction)
```

The diagonal elements indicate correct predictions, while the off-diagonals, incorrect.
52.16% appears to be the success rate of our model, and 47.8% the training error rate.

But, the predictions has been calculated on the Training Data itself, and cannot be relied upon for accuracy against a Test data.

###To overcome this, let's separate the data out into tarining and test data.

```{r}
train <- (Year < 2005)

Smarket.2005 = Smarket[!train, ]
dim(Smarket.2005)

Direction.2005 <- Direction[!train]

```

#### Design a new fit.
```{r}
glm.fit = glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, data= Smarket, family= binomial, subset = train)
glm.probs = predict(glm.fit, Smarket.2005, type = "response")

#Let's compute predictions for 2005
dim(Smarket.2005)
glm.pred = rep("Down", 252)
glm.pred[glm.probs > 0.5] = "Up"

table(glm.pred, Direction.2005)


(77+44)/252
mean(glm.pred==Direction.2005)
```

#### The new model gives an accuracy rate of 48%
The test error rate is 52%.


This does not acutally seem surprising, as was evident from the model fit too. And, it also does not seem to be realistic where one could predict Stock markets based on the previous day's results.

####But, we can at least try to re- fit the model with the predictors, most effective of all.
```{r}
glm.fit = glm(Direction ~ Lag1 + Lag2, data=Smarket, family = binomial, subset = train)
summary(glm.fit)

```

```{r}
glm.probs = predict(glm.fit, newdata=Smarket.2005, type="response")
glm.pred = rep("Down", 252)
glm.pred[glm.probs>0.5] = "Up"

table(glm.pred, Direction.2005)

(35+106)/252
mean(glm.pred==Direction.2005)


```

Test error rate = 44%

#### test a prediction for any test inputs.
```{r}
predict(glm.fit, newdata= data.frame(Lag1=c(1.2, 1.5), Lag2=c(1.1, -0.8)), type="response")

```

