---
title: "Framingham Heart Study"
output:
  html_document: default
  html_notebook: default
---

### Load requried Libraries.
```{r, message=FALSE}
library(dplyr)
library(caTools)
```

### Read the data into R.
```{r}
data <- read.csv("data/framingham.csv")

glimpse(data)
```

#### Data Attributes:
demographic Risk factors: Age, Male, Education
Behavioral: Current smoker, cigs per day
medical history risk factors: BPMeds, prevalentStroke, prevalentHyp, diabetes
Physical exam risk factors: totChol, sysBP, diaBP, BMI, heartRate, glucose
outcome variable: whether or not patient developed CHD in next 10 years.


#### Split the data into training and test sets.
Set the seed, since R generated the sample randomly
Since, we have much data- we can distribute mnore amount of data for Test set.
```{r}
set.seed(1000)
split <- sample.split(data$TenYearCHD, 0.65)

train <- subset(data, split)
test <- subset(data, !split)
```

### Create a model fit
```{r}
glm.fit <- glm(TenYearCHD ~ ., data = train, family = binomial)
summary(glm.fit)

```


#### Make predictions on test data

```{r}
predictTest <- predict(glm.fit, type="response", newdata = test)
table(test$TenYearCHD, predictTest > 0.5)

modelAccuracy = (1070+21)/1484
modelAccuracy
```
Accuracy = 73.52%

#### Compare accuracy to a simple Baseline Method. The more frequent outcome in this case is 0. So, a baseline method will predict a 0, i.e. No CHD.

Accuracy of the baseline method = (1070 + 13)/ 1484 -> 72.9%
Model barely meets the Baseline in terms of Accuracy.

#### Let's compute ROC to measure the accuracy while varying the Threshold.

```{r, message=FALSE}
library(ROCR)
```

```{r}
ROCR_pred <- prediction(predictTest, test$TenYearCHD)
plot(performance(ROCR_pred, "tpr", "fpr"), colorize = TRUE, print.cutoffs.at = seq(0, 1, 0.1), text.adj = c(-0.2, 1.7))


as.numeric(performance(ROCR_pred, "auc")@y.values)
```

This gives the AUC values on a testing set. So, the AUC of 73% means that the model can differentiate between low risk and high Risk patients very well.


### Validate the Model:
Compare the results of FHS with the other Studies which were carried on different populations, and compare the Results for Accuracy.

ARIC Study- White and Black
(Honolulu) HHP - Japanese American
(Peurto Rico) PR- Hispanic
SHS- Native American

