---
title: "GLM on Hospital quality data"
output:
  html_document: default
  html_notebook: default
---

```{r, message=FALSE}
library(caTools)
library(dplyr)


```

#### Collect data and build a model.
```{r}
quality = read.csv("data/quality.csv")
glimpse(quality)

table(quality$PoorCare)

set.seed(88)
split <- sample.split(quality$PoorCare, SplitRatio = 0.75)
qualityTrain <- subset(quality, split)
qualityTest <- subset(quality, !split)

qualityLog <- glm(PoorCare ~ OfficeVisits + Narcotics, data= qualityTrain, family = binomial)
summary(qualityLog)

glm.fit <- glm(PoorCare ~ OfficeVisits + AcuteDrugGapSmall, data = qualityTrain, family = binomial)
summary(glm.fit)

predictTrain <- predict(qualityLog, type="response")
summary(predictTrain)

tapply(predictTrain, qualityTrain$PoorCare, mean)


```

If we consider a threshold of 0.5, Specificity and Sensitivity can be calculated as:

```{r}
table(qualityTrain$PoorCare, predictTrain > 0.5)

Sensitivity = 10/25
Specificity = 70/74


```


Increasing the Threshold of 0.7

```{r}

table(qualityTrain$PoorCare, predictTrain > 0.7)

Sensitivity = 8/25
Specificity = 73/74

```

AS can be seen, by increasing the threshold- Sensitivity went DOWN, and Specificity increased.

Decreasing the Threshold will increase the Sensitivity and lower the Specificity
```{r}

table(qualityTrain$PoorCare, predictTrain > 0.2)

Sensitivity = 16/25
Specificity = 54/74

```


### Select a threshold value using an ROC Curve (Receiver Operator Characteristic Curve)

```{r}
library(ROCR)

ROCR_pred <- prediction(predictTrain, qualityTrain$PoorCare)

ROCR_perf <- performance(ROCR_pred, "tpr", "fpr")
plot(ROCR_perf)

plot(ROCR_perf, colorize = TRUE)

plot(ROCR_perf, colorize = TRUE, print.cutoffs.at = seq(0, 1, 0.1), text.adj=c(-0.2, 1.7))

```


### Make predictions on the Test data:

```{r}
predictTest <- predict(qualityLog, newdata=qualityTest, type = "response")

table(predictTest > 0.5, qualityTest$PoorCare)
tapply(predictTest, qualityTest$PoorCare, mean)

ROCR_test_pred <- prediction(predictTest, qualityTest$PoorCare)
ROCR_test_perf <- performance(ROCR_test_pred, "tpr", "fpr")

plot(ROCR_test_perf, colorize = TRUE, print.cutoffs.at = seq(0,1, 0.1), text.adj = c(-0.1, 2.0))
```

