---
title: "Classification- Linear Discriminant Analysis"
output: html_notebook
---


```{r, message= FALSE}
library(MASS)
library(ISLR)
data(Smarket)

```


```{r}
attach(Smarket)
train <- Year < 2005

Smarket.2005 <- Smarket[!train, ]
Direction.2005 <- Direction[!train]
```

```{r, echo=TRUE}
lda.fit <- lda(Direction ~ Lag1 + Lag2, data = Smarket, subset=train)
lda.fit

plot(lda.fit)
```

From prior probabilities, it can be seen that the market went Down for 49% of the Days, and 51% of times, it went UP.

if -0.642 X Lag1 - 0.514 X Lag2 is large, LDA will predict a market increase, and if it is small, then the LDA classifier will predict a DECLINE.

The plot() prodcues plots of the linear discriminants, obtained by computing -0.642 X Lag1 - 0.514 X Lag2 for each of the training observations.

The rpedict() returns a list with 3 elements. The first element, class, contains LDA's predictions about the movement of the market, posterior prabability that the corresponding observation belongs to the kth class.
Finally, x contains the linear discriminants:

```{r}
lda.pred <- predict(lda.fit, Smarket.2005)
names(lda.pred)

lda.class <- lda.pred$class

table(lda.class, Direction.2005)
mean(lda.class==Direction.2005)

```


```{r}
sum(lda.pred$posterior[, 1] >= 0.5)
sum(lda.pred$posterior[, 1] < 0.5)

lda.pred$posterior[1:20, 1]
lda.class[1:20]
```

If we wanted to use a posterior probability threshold other than 50% for predictions. We could do:
```{r}
sum(lda.pred$posterior[, 1] > 0.9)
```

